\documentclass[../TopologyQualSolutions.tex]{subfiles}

\begin{document}

\section{Unfinished}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fall 2013}

\begin{prob}{F13}{F13.1}
    Show that the fundamental group of the torus $T^2 = S^1 \times S^1$ is $\Z \oplus \Z$ in two distinct ways:

    \begin{enumerate}[(a)]
        \item Describe a cell structure for $T^2$ and use related results to compute its fundamental group.
        \item Describe the universal covering space of $T^2$ and use this description to compute the fundamental group.
    \end{enumerate}
\end{prob}

\begin{prob}{F13}{F13.2}
    Let $S^1$ be the unit complex numbers under multiplication and $U$ an open subset of $S^1 \times S^1$ containing the diagonal
        \[\Delta = \{(x,x): x \in S^1 \times S^1 \}.\]
    Show that there is an open set $W \sq S^1$ containing $1 \in S^1$ such that
        \[V = \{(x,xw): x \in S^1, w \in W\} \]
    is an open set with $\Delta \sq V \sq U$.
\end{prob}

\begin{prob}{F13}{F13.3}
    Prove or provide a counter example to the following:
    \begin{enumerate}[(a)]
        \item The interior of a connected set is connected.
        \item The closure of a path connected set is path connected.
        \item The quotient of a connected set is connected (under the quotient topology).
        \item If $C$ is an infinite collection of connected sets where every pair of sets in $C$ has a non-empty intersection then its union is connected.
    \end{enumerate}
\end{prob}

\begin{solution}
The interior of a connected set need not be connected. Let $X \sq \R^2$ be the closed unit ball with center $(0,1)$ and $Y \sq \R^2$ the closed unit ball with center (0,-1). Then $X \cup Y$ is connected as the set is path-connected. However, the interior of $X \cup Y$ is the union of the corresponding open balls. In this case, the open balls provide a separation meaning that the interior is not connected.
\end{solution}

\begin{solution}
    The clsure of a path connected set need not be path connected. Consider the Topologist's Spiral. Let $X$ denote the spiral and $Y = S^1$ so that the Topologist's Spiral can be written as $X \cup Y$. In this case, $X$ is path-connected, but the closure of $X$ in $X \cup Y$ is $X \cup Y$ which is not path-connected.
\end{solution}

\begin{proof}
    Let $X$ be a connected set and $\sim$ some equivalence relation on $X$. Let $Y = X/\sim$. The quotient map $q: X \to X/\sim$ is a surjective, continuous map. As the continuous image of a connected set is connected, it follows that $X/\sim$ is connected.
\end{proof}

\begin{proof}
    \textcolor{red}{Help!}
\end{proof}

\begin{prob}{F13}{F13.6}
    Let $\{Y_\alpha\}$ be a collection of topological spaces, $Y = \prod_{\alpha} Y_\alpha$ their product under the product topology, and $\pi_\beta: Y \to Y_\beta$ the projection map to the $\beta$th factor of the product. Prove that a function $f: X \to Y$ is continuous if and only if for all $\beta$ the composition $\pi_\beta \circ f: X \to Y_\beta$ is continuous.
\end{prob}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fall 2012}

\begin{prob}{F12}{F12.2}
    Let $X$ be a nonempty set and let $\scr{B} = \scr{B}(X,\R)$ denote the set of bounded real valued functions on $X$. Metrize $\scr{B}$ by setting
        \[d(f,g) = \sup_{x \in X} |f(x) - g(x)|. \]
    Prove that $(\scr{B},d)$ is a complete metric space.
\end{prob}

\begin{prob}{F12}{F12.3}
    \begin{enumerate}[(a)]
        \item Let $X$ be a nonempty set and $B$ a subset of the power set of $X$. Give necessary and sufficient conditions on $B$ such that it is a basis for some topology on $X$.
        \item Let $\{F_i: i \in \N\}$ be a countable collection of finite sets. Show that both of the following form a basis for some topology on the infinite product $\prod F_i$.
        \begin{enumerate}[(i)]
            \item All the sets of the form $\prod U_i$ where each $U_i \sq F_i$.
            \item All the sets of the form $\prod U_i$ where $U_i \sq F_i$ and $U_i = F)i$ except for possibly finitely many $i$.
        \end{enumerate}
        \item Show that the set $\prod F_i$ equipped with the topology from (i) need not be homeomorphic to the set $\prod F_i$ equipped with the topology from (ii).
    \end{enumerate}
\end{prob}

\begin{prob}{F12}{F12.4}
    Let $X,Y$ be non-empty topological spaces.
    \begin{enumerate}[(a)]
        \item Define the product topology on $X \times Y$.
        \item Define path connected.
        \item Show that $X$ and $Y$ are path connected if and only if $X \times Y$ is path connected.
    \end{enumerate}
\end{prob}

See \ref{prob:S12.2} for the definition.

A topological space $X$ is path connected if for any two points $x,y \in X$, there exists a continuous function $\gamma: [0,1] \to X$ where $\gamma(0) = x$ and $\gamma(1) = y$. Here, $\gamma$ is a path.

\begin{proof}
    Assume that $X$ and $Y$ are both path connected. Let $(x_1,y_1),(x_2,y_2) \in X \times Y$ be arbitrary. Since $x_1, x_2 \in X$, there exists a path $\alpha: [0,1] \to X$ with $\alpha(0) = x_1$ and $\alpha(1) = x_2$. Similarly, since $y_1,y_2 \in Y$ there exists a path $\beta: [0,1] \to Y$ where $\beta(0) = y_1$ and $\beta(1) = y_2$. Define $\gamma: [0,1] \to X \times Y$ be $\gamma(t) = (\alpha(t), \beta(t))$. Observe that $\gamma(0) = (x_1,y_1)$ and $\gamma(1) = (x_2,y_2)$. Furthermore, $\gamma$ is continuous as each of its component functions is continuous. Thus, $\gamma$ is a path in $X \times Y$ between $(x_1,y_1)$ and $(x_2,y_2)$. As these points were arbitrary, $X \times Y$ is path connected.
\end{proof}

\begin{prob}{F12}{F12.5}
    Give a careful definition of a connected topological space.
    \begin{enumerate}[(a)]
        \item Prove that the closed interval [0,1] is connected.
        \item Show that a connected metric space with at least two points is uncountable.
    \end{enumerate}
\end{prob}

\begin{prob}{F12}{F12.6}
    Let $X$ be a connected Hausdorff space and $Y = X \cup \{p\}$ with $p \not\int X$. Define a topology $\scr{T}$ on $Y$ which has a basis consisting of open sets in $X$ together with all sets of the form $V \cup \{p\}$ where $V$ is the complement of a compact subset of $X$. Prove that $(Y,\scr{T})$ is
    \begin{enumerate}[(a)]
        \item compact
        \item Hausdorff if and only if $X$ is locally compact.
        \item connected if and only if $X$ is not compact.
    \end{enumerate}
\end{prob}

\begin{prob}{F12}{F12.8}
    Let $\R^2 - \{(0,0)\}$ be the plane punctured at the origin, equipped with the usual topology. Define an equivalence relation on $X$ by $(x,y) \sim (tx,ty)$ for any $t > 0$. Let $Y = X/\sim$ under the quotient topology. Prove that $Y$ is homeomorphic to $S^1$.
\end{prob}

\begin{proof}
    Let $f: Y \to S^1$ be given by $f([v]) = \frac{v}{\norm[v]}$. Let $g: S^1 \to Y$ be given by $g(v) = [v]$. To see that $f$ is well-defined, suppose that $v = tv$ for some $t > 0$. Then, $\norm[tv] = t\norm[v]$ and therefore
        \[f([v]) = \frac{v}{\norm[v]} = \frac{tv}{t\norm[v]} = f([tv]).\]
    Also, $f\circ g(v) = f[v] = \frac{v}{\norm[v]} = v$ since $\norm[v] = 1$ whenever $v \in S^1$. Similarly, $g\circ f([v]) = g\left( \frac{v}{\norm[v]} \right) = \left[\frac{v}{\norm[v]}\right] = [v]$. Therefore $f$ is a bijection. 
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spring 2012}

\begin{prob}{S12.1}{S12.1}
    \begin{enumerate}[(a)]
        \item Define what it means for a topological space to be connected.
        \item Suppose that $H$ is a connected subspace of a topological space $X$ and that $H \sq K \sq \cl{H}$. Show that $K$ is connected.
        \item Suppose that $U$ is a connected open subset of $C[0,1]$ with the $\sup$ metric. Prove that $U$ is path-connected.
    \end{enumerate}
\end{prob}

A topological space $X$ is disconnected if there exist open sets $A,B$ with $A \cap B = \varnothing$ and $X = A \sqcup B$. A space $X$ is connected if it is not disconnected.

\begin{proof}
\end{proof}


\begin{prob}{S12.5}{S12.5}
    Let $X$ be a metric space.
    \begin{enumerate}[(a)]
        \item Suppose that there exists $\epsilon > 0$ such that every $B(x,\epsilon)$ has compact closure. Prove that $X$ is complete.
        \item Suppose that for each $x\in X$ there exists $\epsilon_x > 0$ so that $B(x,\epsilon_x)$ has compact closure. Give an example to show that $X$ need not be complete.
    \end{enumerate}
\end{prob}

\begin{prob}{S12}{S12.6}
    \emph{Covering space problem!}
\end{prob}

\begin{prob}{S12.7}{S12.7}
    Define a metric $d$ on $N = \N \cup \{0\}$ by
        \[d(x,y) = 0\]
    whenever $x = y$ and otherwise
        \[d(x,y) = 5^{-k}\]
    where $5^k$ is the largest power of 5 that divides $|x-y|$.

    \begin{enumerate}[(a)]
        \item Verify that $d$ is a metric.
        \item Give an example of a sequence that converges to 0.
        \item Prove or disprove: The space $(N, d)$ is compact.
        \item Prove or disprove: The set of prime numbers greater than 103 is open in $(N,d)$.
    \end{enumerate}
\end{prob}

\subsection{Fall 2020}


\begin{prob}{F20.3}{F20.3}
Let $(X,d)$ be a metric space and let $f: X \to X$ be a continuous function without any fixed points.
\begin{enumerate}[(i)]
\item If $X$ is compact, show that there exists $\epsilon > 0$ so that $d(x,f(x)) > \epsilon$ for all $x \in X$.
\item Show that this fails if $X$ is not compact.
\end{enumerate}
\end{prob}

\begin{prob}{F20}{F20.7}
A subset $E$ of a topological space $X$ is called a $G_\delta$ if there is a sequence $U_1, U_2, \ldots$ of open subsets of $X$ such that $E = \cap_{j}U_j$.
\begin{enumerate}[(i)]
\item Show that if $f: X \to \R$ is a continuous function from $X$ to the real line, then $\{x: f(x)=0\}$ is closed and is a $G_\delta$.
\item Show that in a metric space, every closed set is a $G_\delta$.
\item Prove  that $(ii)$ fails in an arbitrary topological space.
\end{enumerate}
\end{prob}

\subsection{Spring 2020}

\begin{prob}{S20}{}
Prove that the product of two regular spaces is regular.
\end{prob}

\begin{prob}{S20}{}
A topological space is called \emph{totally disconnected} if every pair of points is contained in a pair of disjoint open sets whose union is the whole space. Prove that every countable metric space is totally disconnected.
\end{prob}

\begin{prob}{S20}{}
Let $X$ be a compact metric space. Prove that there exists a finite set of points $x_1, \ldots, x_n$ such that every point in $X$ is distance less than 3 from some $x_i$ and $d(x_i,x_j) \geq 1$ for any $i \neq j$.
\end{prob}

\subsection{Fall 2016}

\begin{prob}{F16}{F164}
A topological space $X$ is \emph{regular} is for every closed subset $C$ of $X$ and point $p \in X \sm C$, there are disjoint open sets $U, V \sq X$ with $C \sq U$ and $p \in V$. Prove that every compact Hausdorff space is regular.
\end{prob}

\begin{prob}{F16}{}
For each of the following either give a proof or provide a justified counterexample.
\begin{enumerate}[(a)]
\item Suppose that $A$ and $B$ are non-empty topological spaces and $A \times B$ is equipped with the product topology. Let $\sim$ be the equivalence relation on $A \times B$ defined by $(a,b) \sim (a', b')$ if and only if $b = b'$. Is $A \times B/\sim$ homeomorphic to $A$?
\item Suppose that $B$ and $C$ are subspaces of a topological space $A$. If $B$ is homeomorphic to $C$, does it follow that $A/B$ is homeomorphic to $A/C$?
\end{enumerate}
\end{prob}
    
\begin{prob}{F16}{}
State the contraction mapping theorem. Prove there is a unique continuous function $f: [0,1] \to [0,1]$ that satisfies
    \[f(x) = \frac{f(\sin x) + \cos x}{2} \]
for all $x \in [0,1]$.
\end{prob}


\begin{prob}{S20}{}
A topological space is \emph{separable} if it has a countable dense subset. Prove that the product of countable collection of separable topological spaces is separable.
\end{prob}

\begin{prob}{F20}{F20.2}
Let $X$ be a topological space. Show that the intersection of any two dense open sets in $X$ is also dense. Give an example that shows that this may fail if the two sets are not required to be open.
\end{prob}



\begin{prob}{F20}{F20.5}
\begin{enumerate}[(i)]
\item Suppose that $X$ is a topological space with the property that every two point space lies in a connected subspace of $X$. Prove that $X$ is connected.
\item Suppose that the work \textbf{TOPOLOGY} is written in purple ink on a square of white paper. Let $V$ denote the subspace consisting of the white paper that remains. How many path-connected components  does $V$ have? For each such component $X$, compute $\pi_1(X)$.
\end{enumerate}
\end{prob}

\begin{prob}{F20}{F20.6}
Suppose that $X$ is a metric space. Define what it means for $C \sq X$ to be \emph{complete}.
\begin{enumerate}[(i)]
\item Show that if $C$ and $D$ are complete subsets of $X$ then $C\cup D$ is complete.
\item Suppose that $\{C_\lambda\}$ is a family of complete subspaces of $X$. Prove that $\cap_{\lambda} C_{\lambda}$ is either empty or complete.
\end{enumerate}
\end{prob}


\begin{prob}{F19}{}
Give careful definitions of \emph{continuity} and \emph{uniform continuity} for maps between metric spaces.
\begin{enumerate}[(i)]
\item Show that if $f: X \to Y$ is a continuous map between metric spaces and $X$ is compact, then $f$ is uniformly continuous.
\item Prove or disprove: If $f: X \to Y$ is a uniformly continuous map between metric spaces and $X$ is complete, then $Y$ is complete.
\end{enumerate}
\end{prob}

\begin{prob}{F19}{}
Are the following true or false? Give a proof or counter-example.
\begin{enumerate}[(a)]
\item If $X = U \cup V$ where $U$ and $V$ are both open and simply connected, then $X$ is simply connected.
\item If $f: X \to Y$ is a continuous map which is onto, then $f_*: \pi_1(X) \to \pi_1(Y)$ is onto.
\item If $f: X \to Y$ is a continuous map which is injective, then $f_*: \pi_1(X) \to \pi_1(Y)$ is injective.
\end{enumerate}
\end{prob}

\begin{prob}{F19}{}
Given $\epsilon>0$, two points $a,b$ of a metric space $M$ are said to be \emph{connected by an $\epsilon$-chain}, if there exist points $x_0, \ldots, x_n \in M$ such that $x_0 = a$, $x_n = b$ and $d(x_i, x_{i+1}) < \epsilon$ for each $i = 0, \ldots, n-1$.
\begin{enumerate}[(a)]
\item Show that if $M$ is connected, then for every $\epsilon > 0$ any two points are connected by an $\epsilon$-chain. Provide an example to show that the converse does not hold.
\item Show that if $M$ is a compact metric space and for every $\epsilon > 0$ any two points  of $M$ are connected by an $\epsilon$-chain, then $M$ is connected.
\end{enumerate}
\end{prob}

\end{document}